Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
include different types of AR in Shiny App

#
# Generating asocciation rules
AR <- my_apriori(transactions)

@@

AR_Taken <- my_apriori(transactions_Taken)

#
# Save association rules
AR <- list(
    AR = AR,
    AR_PF = AR_PF,
    AR_HL = AR_HL,
    AR_Taken = AR_Taken
    )

save(AR, file = "App/AR.RDATA")

@@

### CSPADE Algorithm
We apply cspade algorithm

```{r}
# Transform rules from ruleInduction into a readable data frame
clean_IR <- function(rules){
  rules %>%
    as("data.frame") %>%
    # filter(
    #   count >= 1
    # ) %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]"),
      `rhs.support` = confidence / lift
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=") %>%
    mutate_at(
      c("support", #"lhs.support",
        "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, 
      #count, lhs.support, #figure out how to get these
      confidence, rhs.support,
      lift
    ) #%>%
    #arrange(
    #  desc(count)
    #)

}
```
We apply cspade followed by rule induction
```{r}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_IR <- function(data){
  data %>%
  cspade(
    parameter = list(
      support = 0.01, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4, # max time difference between consecutive element of a sequence
      maxwin  = 1e4  # max time difference between any two elements of a sequence
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      confidence = 0, #we need to play with the parameters.
      control    = list(verbose = FALSE)
      ) %>%
    clean_IR
}

#Generating induced rules
IR    <- my_IR(data = sequences   )
IR_PF <- my_IR(data = sequences_PF)
IR_HL <- my_IR(data = sequences_HL)

#Saving induced rules:
save(
  IR = list(
    IR = IR,
    IR_PF = IR_PF,
    IR_HL = IR_HL
    ),
  file = "Output/IR.RDATA")

rm(clean_IR, my_IR,
   sequences, sequences_PF, sequences_HL,
   IR, IR_PF, IR_HL)

@@

##calculate appropriate measures:
```{r}
n_students <- length(unique(d_sequence_transactions$`Student ID`))

>>>>

#
# Generating asocciation rules
AR_taken <- my_apriori(transactions)

@@

AR_not_taken <- my_apriori(transactions_Taken)

#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken,
     file = "App/ARR.RDATA")

@@

### CSPADE Algorithm

```{r}

subsequences <- sequences %>%
  cspade(
    parameter = list(
      support = 0.01, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4, # max time difference between consecutive element of a sequence
      maxwin  = 1e4  # max time difference between any two elements of a sequence
      ),
    control = list(
      verbose = FALSE
      )
    )

#Inspect results CSPADE
summary(subsequences)
as(subsequences, "data.frame")
```

##rule induction:
```{r}
rules <- ruleInduction(subsequences,
                       confidence = 0, #we need to play with the parameters.
                       control    = list(verbose = TRUE))

pass_rules_df <- as(rules, "data.frame") %>%

  separate(sequece, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns

#  filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment

  arrange(
    LHS, RHS,
    desc(confidence), desc(lift))

@@

```{r}

# Transform AR from apriori into a readable data frame
clean_rules <- function(rules){
  rules %>%
    as("data.frame") %>%
    # filter(
    #   count >= 1
    # ) %>%
    mutate(`rhs.support` = confidence / lift) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=>") %>%
    mutate(
      lhs = str_remove(lhs, pattern = "[<]"),
      lhs = str_remove(lhs, pattern = "[{]"),
      lhs = str_remove(lhs, pattern = "[}]"),
      lhs = str_remove(lhs, pattern = "[>]"),
      rhs = str_remove(rhs, pattern = "[<]"),
      rhs = str_remove(rhs, pattern = "[{]"),
      rhs = str_remove(rhs, pattern = "[}]"),
      rhs = str_remove(rhs, pattern = "[>]")
    ) %>%
    mutate_at(
      c("support", #"lhs.support",
        "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, #count, lhs.support,
      confidence, rhs.support,
      lift
    ) #%>%
    #arrange(
    #  desc(count)
    #)

}
```
##calculate appropriate measures:
```{r}
n_students <- length(unique(d_sequence_transactions$`Student ID`))
